Self Regulation Ontology Retest Analyses

### 2018-08-06 code/SRO_Retest_Analyses.Rmd
fixed survey names for boot task level plot

#Manual correction
tmp = tmp %>%
  mutate(task = ifelse(task_group == 'holt laury survey', "task", as.character(task))) %>%
  mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
  mutate(task_group = gsub("survey", "", task_group))
```

>>>>

#Manual correction
tmp = tmp %>%
  mutate(task = ifelse(task_group == 'holt laury survey', "task", as.character(task))) %>%
  mutate(task_group = gsub("survey", "", task_group),
         task_group = gsub("task", "", task_group),
         task_group = str_to_title(task_group)) %>%
  mutate(task_group = ifelse(task_group == "Psychological Refractory Period Two Choices", "Psychological Refractory Period", ifelse(task_group == "Angling Risk Always Sunny", "Angling Risk", ifelse(task_group == "Two Stage", "Two Step", ifelse(task_group == "Threebytwo", "Task Switching", ifelse(task_group == "Adaptive N Back", "Adaptive N-back", ifelse(task_group == "Go Nogo", "Go/No-go",  ifelse(task_group == "Ravens", "Raven's", task_group)))))))) %>%
  mutate(task_group = ifelse(task_group == "Bis Bas ", "BIS-BAS", ifelse(task_group == "Bis11 ", "BIS-11", ifelse(task_group == "Dospert Eb ", "DOSPERT EB", ifelse(task_group == "Dospert Rp ", "DOSPOERT RP", ifelse(task_group == "Dospert Rt ", "DOSPERT RT", ifelse(task_group == "Erq ", "ERQ", ifelse(task_group == "Upps Impulsivity ", "UPPS-P", task_group))))))))
```

```{r}
trial_num_info = tmp %>%
  group_by(task_group) %>%
  summarise(mean_num_all_trials = round(mean(num_all_trials)),
            num_measures = length(unique(dv)))

tmp = tmp %>%
  left_join(trial_num_info, by="task_group")
```
